## The `pRolocdata` `hyperLOPIT` data, as csv files

This data originates from the Bioconductor
[`pRolocdata`](http://bioconductor.org/packages/release/data/experiment/html/pRolocdata.html)
package. It is a recent spatial proteomics dataset, formatted and
analysed using the
[`pRoloc`](http://bioconductor.org/packages/release/bioc/html/pRoloc.html)
software.

#### Installation

To install these software:

```r
source("https://bioconductor.org/biocLite.R")
biocLite("pRoloc")
biocLite("pRolocdata")
```

#### Accessing the data

```{r demo, warning=FALSE}
suppressPackageStartupMessages(library("pRolocdata"))
data(hyperLOPIT2015)
class(hyperLOPIT2015)
hyperLOPIT2015
```

This `MSnSet` class is specific to quantitative proteomics data, but
that canb be summerised by 2 or 3 tabular data structures (from an R
point of view, 1 [expression `matrix`](./exprs.csv) and 1 or 2
`data.frames` describing the [features](./fdata/csv) and
[samples](./pdata.csv)), which are accessible individually with

```{r exprs}
exprs(hyperLOPIT2015)[1:6, 1:3] ## a matrix
```

```{r fdata}
fData(LOPIT2015)[1:6, 1:3] ## a data.frame
```

```{r pdata}
pData(hyperLOPIT2015)[1:6, 1:3] ## second data.frame
```

#### Producing the csv files

```{r makecsv}
write.csv(exprs(hyperLOPIT2015), file = "exprs.csv")
write.csv(fData(hyperLOPIT2015), file = "fdata.csv")
write.csv(pData(hyperLOPIT2015), file = "pdata.csv")
```

#### Session information

```{r si}
sessionInfo()
```
